---
title: "R Notebook"
output: html_notebook
---

Question: Are there differences in IBS between different type of sharing?

Here we test two sync measures: CCORR and ISPC/PLV

Here we test 4 ROIs: frontal, temporal, parietal, occipital\
frontal - F3, F4, F7, F8, Fz, AFz\
parietal - P3, P4, P7, P8, Pz, CPz\
temporal - T7, T8\
occipital - O1, O2\

Here we test three frequency bands: theta, alpha, beta\
theta (3-7 Hz)\
alpha (8-12 Hz)\
beta (14-30 Hz)\

First I compare Resting state 1 (baseline) with sharing conditions. In case there is a difference between baseline and sharing condition for a particulare ROI, Frequency, Sync measure, I follow it up with 2x2 comparison between types of sharing (emotional/neutral) and order of sharing (first emotional/neutral).


load required libraries\
```{r}
library(lme4)
library(lmerTest)
library(tidyr)
library(ggplot2)
library(ggthemes)
```

remove warnings
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

load data\
add info about ROIs\
add info about bands
add info about sync measures\
rename variables\
concatenate in one data.frame\
subset data to resting state 1, emotional sharing, neutral sharing\

```{r}
list_all_files <-list.files("./csv_files_ccor/",full.names = TRUE)
d<-do.call("rbind",lapply(list_all_files,read.csv, header=FALSE))

ROIs <- c('frontal', 'temporal', 'parietal', 'occipital')
bands <-c('theta', 'alpha', 'beta_')
sync_measures <- c('ccorr', 'p_cor', 'ispc.', 'amenv')


freq<-c()
condition<-c()
sync <-c()
for (rowi in 1:60){
  freq_tmp <- substr(list_all_files[rowi],21,25)
  freq_tmp <- rep(freq_tmp,36)
  freq <- c(freq,freq_tmp)

  condition_tmp <- substr(list_all_files[rowi],18,19)
  condition_tmp <- rep(condition_tmp, 36)
  condition<-c(condition,condition_tmp)
  
  sync_measures_tmp <- substr(list_all_files[rowi],27,31)
  sync_measures_tmp <-  rep(sync_measures_tmp,36)
  sync <- c(sync, sync_measures_tmp)
  
}


d_pairs_order <- read.csv('order_pairs.csv')

order_pairs <- rep(d_pairs_order$FirstSharing, 60)
pair_numbers <- rep(1:36,60)
d<-cbind(d,order_pairs,pair_numbers,freq,condition, sync)
colnames(d)[1:4]<-ROIs
colnames(d)[5]<-'FirstSharing'
colnames(d)[6] <- 'pair'

d <- gather(d, ROI, IBS, frontal:occipital,factor_key = TRUE)

d <- d[d$condition == 'R1' | d$condition == 'ES' | d$condition == 'NS', ]
d$condition <- factor(d$condition)



```

change variables for modelling\

Sharing\
resting state  -.5\
sharing         .5\
 
SharingOrder\
E first    -.5
N firts     .5



```{r}

d$freq <- as.factor(d$freq)
d$condition <- as.factor(d$condition)
d$sync <- as.factor(d$sync)
d$FirstSharing <- as.factor(d$FirstSharing)

for (irow in 1:nrow(d)){
  if (d$condition[irow] == 'R1'){
    d$Sharing[irow] <- -.5
    d$SharingPLOT[irow] <- 'Resting state'
  }
  else if (d$condition[irow] == 'ES'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
  else if (d$condition[irow] == 'NS'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
} 

for (irow in 1:nrow(d)){
  if (d$FirstSharing[irow] == 'E'){
    d$SharingOrder[irow] <- -.5
  }
  else if (d$FirstSharing[irow] == 'N'){
    d$SharingOrder[irow] <- .5
  }
} 

```

CCORR REAL PAIRS

Here I would like to point (visually) that differences (statistical) between resting state 1 (baseline) are not in our favor. Only in Theta (frontal, temporal) IBS is higher in Sharing conditions than Baseline. 
In alpha (all ROIs) and beta (temporal, parietal, occipital) IBS is higher in baseline. 

```{r}
d_ccorr <- d[d$sync == 'ccorr',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```

ISPC REAL PAIRS

Parietal difference in alpha and beta is also stronger for baseline than sharing conditions


```{r}
d_ccorr <- d[d$sync == 'ispc.',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```


SUDO DATA

```{r}
list_all_files <-list.files("./csv_files_ccor_SUDO/",full.names = TRUE)
d<-do.call("rbind",lapply(list_all_files,read.csv, header=FALSE))

ROIs <- c('frontal', 'temporal', 'parietal', 'occipital')
bands <-c('theta', 'alpha', 'beta_')
sync_measures <- c('ccorr', 'p_cor', 'ispc.', 'amenv')


freq<-c()
condition<-c()
sync <-c()
for (rowi in 1:60){
  freq_tmp <- substr(list_all_files[rowi],26,30)
  freq_tmp <- rep(freq_tmp,36)
  freq <- c(freq,freq_tmp)

  condition_tmp <- substr(list_all_files[rowi],23,24)
  condition_tmp <- rep(condition_tmp, 36)
  condition<-c(condition,condition_tmp)
  
  sync_measures_tmp <- substr(list_all_files[rowi],32,36)
  sync_measures_tmp <-  rep(sync_measures_tmp,36)
  sync <- c(sync, sync_measures_tmp)
  
}


d_pairs_order <- read.csv('order_pairs.csv')

order_pairs <- rep(d_pairs_order$FirstSharing, 60)
pair_numbers <- rep(1:36,60)
d<-cbind(d,order_pairs,pair_numbers,freq,condition, sync)
colnames(d)[1:4]<-ROIs
colnames(d)[5]<-'FirstSharing'
colnames(d)[6] <- 'pair'

d <- gather(d, ROI, IBS, frontal:occipital,factor_key = TRUE)

d <- d[d$condition == 'R1' | d$condition == 'ES' | d$condition == 'NS', ]
d$condition <- factor(d$condition)



```

change variables for modelling\

Sharing\
resting state  -.5\
sharing         .5\
 
SharingOrder\
E first    -.5
N firts     .5



```{r}

d$freq <- as.factor(d$freq)
d$condition <- as.factor(d$condition)
d$sync <- as.factor(d$sync)
d$FirstSharing <- as.factor(d$FirstSharing)

for (irow in 1:nrow(d)){
  if (d$condition[irow] == 'R1'){
    d$Sharing[irow] <- -.5
    d$SharingPLOT[irow] <- 'Resting state'
  }
  else if (d$condition[irow] == 'ES'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
  else if (d$condition[irow] == 'NS'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
} 

for (irow in 1:nrow(d)){
  if (d$FirstSharing[irow] == 'E'){
    d$SharingOrder[irow] <- -.5
  }
  else if (d$FirstSharing[irow] == 'N'){
    d$SharingOrder[irow] <- .5
  }
} 

```

CCORR SUDO PAIRS

Here I would like to point (visually) that differences (statistical) between resting state 1 (baseline) are not in our favor. Only in Theta (frontal, temporal) IBS is higher in Sharing conditions than Baseline. 
In alpha (all ROIs) and beta (temporal, parietal, occipital) IBS is higher in baseline. 

```{r}
d_ccorr <- d[d$sync == 'ccorr',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```

ISPC SUDO PAIRS

Parietal difference in alpha and beta is also stronger for baseline than sharing conditions


```{r}
d_ccorr <- d[d$sync == 'ispc.',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```



