---
title: "R Notebook"
output: html_notebook
---

Question: Are there differences in IBS between different type of sharing?

Here we test two sync measures: CCORR and ISPC/PLV

Here we test 4 ROIs: frontal, temporal, parietal, occipital\
frontal - F3, F4, F7, F8, Fz, AFz\
parietal - P3, P4, P7, P8, Pz, CPz\
temporal - T7, T8\
occipital - O1, O2\

Here we test three frequency bands: theta, alpha, beta\
theta (3-7 Hz)\
alpha (8-12 Hz)\
beta (14-30 Hz)\

First I compare Resting state 1 (baseline) with sharing conditions. In case there is a difference between baseline and sharing condition for a particulare ROI, Frequency, Sync measure, I follow it up with 2x2 comparison between types of sharing (emotional/neutral) and order of sharing (first emotional/neutral).


load required libraries\
```{r}
library(lme4)
library(lmerTest)
library(tidyr)
library(ggplot2)
library(ggthemes)
```

remove warnings
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

load data\
add info about ROIs\
add info about bands
add info about sync measures\
rename variables\
concatenate in one data.frame\
subset data to resting state 1, emotional sharing, neutral sharing\

```{r}
list_all_files <-list.files("./csv_files_ccor/",full.names = TRUE)
d<-do.call("rbind",lapply(list_all_files,read.csv, header=FALSE))

ROIs <- c('frontal', 'temporal', 'parietal', 'occipital')
bands <-c('theta', 'alpha', 'beta_')
sync_measures <- c('ccorr', 'p_cor', 'ispc.', 'amenv')


freq<-c()
condition<-c()
sync <-c()
for (rowi in 1:60){
  freq_tmp <- substr(list_all_files[rowi],21,25)
  freq_tmp <- rep(freq_tmp,36)
  freq <- c(freq,freq_tmp)

  condition_tmp <- substr(list_all_files[rowi],18,19)
  condition_tmp <- rep(condition_tmp, 36)
  condition<-c(condition,condition_tmp)
  
  sync_measures_tmp <- substr(list_all_files[rowi],27,31)
  sync_measures_tmp <-  rep(sync_measures_tmp,36)
  sync <- c(sync, sync_measures_tmp)
  
}


d_pairs_order <- read.csv('order_pairs.csv')

order_pairs <- rep(d_pairs_order$FirstSharing, 60)
pair_numbers <- rep(1:36,60)
d<-cbind(d,order_pairs,pair_numbers,freq,condition, sync)
colnames(d)[1:4]<-ROIs
colnames(d)[5]<-'FirstSharing'
colnames(d)[6] <- 'pair'

d <- gather(d, ROI, IBS, frontal:occipital,factor_key = TRUE)

d <- d[d$condition == 'R1' | d$condition == 'ES' | d$condition == 'NS', ]
d$condition <- factor(d$condition)



```

change variables for modelling\

Sharing\
resting state  -.5\
sharing         .5\
 
SharingOrder\
E first    -.5
N firts     .5



```{r}

d$freq <- as.factor(d$freq)
d$condition <- as.factor(d$condition)
d$sync <- as.factor(d$sync)
d$FirstSharing <- as.factor(d$FirstSharing)

for (irow in 1:nrow(d)){
  if (d$condition[irow] == 'R1'){
    d$Sharing[irow] <- -.5
    d$SharingPLOT[irow] <- 'Resting state'
  }
  else if (d$condition[irow] == 'ES'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
  else if (d$condition[irow] == 'NS'){
    d$Sharing[irow] <- .5
    d$SharingPLOT[irow] <- 'Sharing'
      }
} 

for (irow in 1:nrow(d)){
  if (d$FirstSharing[irow] == 'E'){
    d$SharingOrder[irow] <- -.5
  }
  else if (d$FirstSharing[irow] == 'N'){
    d$SharingOrder[irow] <- .5
  }
} 

```

1. CCorr

subset data to ccorr
```{r}
d_ccorr <- d[d$sync == 'ccorr',]
d_ccorr$sync <- factor(d_ccorr$sync)

```

A. theta\
subset data to ccorr theta\

```{r}
d_ccorr_theta <- d_ccorr[d_ccorr$freq == 'theta',]
d_ccorr_theta$freq <- factor(d_ccorr_theta$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

DIFFERENCE

```{r}
d_ccorr_theta_frontal <- d_ccorr_theta[d_ccorr_theta$ROI == 'frontal',]
d_ccorr_theta_frontal$ROI <- factor(d_ccorr_theta_frontal$ROI)

model_ccorr_theta_frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_theta_frontal)
summary(model_ccorr_theta_frontal)
```
Subset data to temporal\
model\
summary model\

**TEMPORAL**

DIFFERENCE

```{r}
d_ccorr_theta_temporal <- d_ccorr_theta[d_ccorr_theta$ROI == 'temporal',]
d_ccorr_theta_temporal$ROI <- factor(d_ccorr_theta_temporal$ROI)

model_ccorr_theta_temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_theta_temporal)
summary(model_ccorr_theta_temporal)
```
Subset data to parietal\
model\
summary model\

**PARIETAL**

NO DIFFERENCE

```{r}
d_ccorr_theta_parietal <- d_ccorr_theta[d_ccorr_theta$ROI == 'parietal',]
d_ccorr_theta_parietal$ROI <- factor(d_ccorr_theta_parietal$ROI)

model_ccorr_theta_parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_theta_parietal)
summary(model_ccorr_theta_parietal)
```
Subset data to occipital\
model\
summary model\

**OCCIPITAL**

NO DIFFERENCE

```{r}
d_ccorr_theta_occipital <- d_ccorr_theta[d_ccorr_theta$ROI == 'occipital',]
d_ccorr_theta_occipital$ROI <- factor(d_ccorr_theta_occipital$ROI)

model_ccorr_theta_occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_theta_occipital)
summary(model_ccorr_theta_occipital)
```



We follow up with differences between sharing conditions

subset data to ccorr only sharing

```{r}
d_ccorr_s_theta <- d_ccorr_theta[d_ccorr_theta$condition == 'ES' | d_ccorr_theta$condition == 'NS' ,]
d_ccorr_s_theta$condition <- factor(d_ccorr_s_theta$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ccorr_s_theta)){
  if (d_ccorr_s_theta$condition[irow] == 'ES'){
    d_ccorr_s_theta$condition_model[irow] <- -.5
  }
  else if (d_ccorr_s_theta$condition[irow] == 'NS'){
    d_ccorr_s_theta$condition_model[irow] <- .5
  }
} 


```


Subset data to frontal\
model\
summary model\

**FRONTAL**

NO DIFFERENCE
```{r}
d_ccorr_s_theta_frontal <- d_ccorr_s_theta[d_ccorr_s_theta$ROI == 'frontal',]
d_ccorr_s_theta_frontal$ROI <- factor(d_ccorr_s_theta_frontal$ROI)

model_ccorr_s_theta_frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_theta_frontal)
summary(model_ccorr_s_theta_frontal)
```



Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ccorr_s_theta_temporal <- d_ccorr_s_theta[d_ccorr_s_theta$ROI == 'temporal',]
d_ccorr_s_theta_temporal$ROI <- factor(d_ccorr_s_theta_temporal$ROI)

model_ccorr_s_theta_temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_theta_temporal)
summary(model_ccorr_s_theta_temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE between emotional and neutral sharing! 
```{r}
d_ccorr_s_theta_parietal <- d_ccorr_s_theta[d_ccorr_s_theta$ROI == 'parietal',]
d_ccorr_s_theta_parietal$ROI <- factor(d_ccorr_s_theta_parietal$ROI)

model_ccorr_s_theta_parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_theta_parietal)
summary(model_ccorr_s_theta_parietal)
```

Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE
```{r}
d_ccorr_s_theta_occipital <- d_ccorr_s_theta[d_ccorr_s_theta$ROI == 'occipital',]
d_ccorr_s_theta_occipital$ROI <- factor(d_ccorr_s_theta_occipital$ROI)

model_ccorr_s_theta_occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_theta_occipital)
summary(model_ccorr_s_theta_occipital)
```

PLOT CCORR THETA

```{r}
plotIBS <- ggplot(data=d_ccorr_theta, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('Ccorr theta')
plotIBS
```

B. alpha\
subset data to ccorr alpha\

```{r}
d_ccorr_alpha <- d_ccorr[d_ccorr$freq == 'alpha',]
d_ccorr_alpha$freq <- factor(d_ccorr_alpha$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

DIFFERENCE

```{r}
d_ccorr_alpha_frontal <- d_ccorr_alpha[d_ccorr_alpha$ROI == 'frontal',]
d_ccorr_alpha_frontal$ROI <- factor(d_ccorr_alpha_frontal$ROI)

model_ccorr_alpha_frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_alpha_frontal)
summary(model_ccorr_alpha_frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

DIFFERENCE

```{r}
d_ccorr_alpha_temporal <- d_ccorr_alpha[d_ccorr_alpha$ROI == 'temporal',]
d_ccorr_alpha_temporal$ROI <- factor(d_ccorr_alpha_temporal$ROI)

model_ccorr_alpha_temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_alpha_temporal)
summary(model_ccorr_alpha_temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE

```{r}
d_ccorr_alpha_parietal <- d_ccorr_alpha[d_ccorr_alpha$ROI == 'parietal',]
d_ccorr_alpha_parietal$ROI <- factor(d_ccorr_alpha_parietal$ROI)

model_ccorr_alpha_parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_alpha_parietal)
summary(model_ccorr_alpha_parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

DIFFERENCE

```{r}
d_ccorr_alpha_occipital <- d_ccorr_alpha[d_ccorr_alpha$ROI == 'occipital',]
d_ccorr_alpha_occipital$ROI <- factor(d_ccorr_alpha_occipital$ROI)

model_ccorr_alpha_occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_alpha_occipital)
summary(model_ccorr_alpha_occipital)
```





subset data to ccorr only sharing

```{r}
d_ccorr_s_alpha <- d_ccorr_alpha[d_ccorr_alpha$condition == 'ES' | d_ccorr_alpha$condition == 'NS' ,]
d_ccorr_s_alpha$condition <- factor(d_ccorr_s_alpha$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ccorr_s_alpha)){
  if (d_ccorr_s_alpha$condition[irow] == 'ES'){
    d_ccorr_s_alpha$condition_model[irow] <- -.5
  }
  else if (d_ccorr_s_alpha$condition[irow] == 'NS'){
    d_ccorr_s_alpha$condition_model[irow] <- .5
  }
} 


```


Subset data to frontal\
model\
summary model\

**FRONTAL**

NO DIFFERENCE

```{r}
d_ccorr_s_alpha_frontal <- d_ccorr_s_alpha[d_ccorr_s_alpha$ROI == 'frontal',]
d_ccorr_s_alpha_frontal$ROI <- factor(d_ccorr_s_alpha_frontal$ROI)

model_ccorr_s_alpha_frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_alpha_frontal)
summary(model_ccorr_s_alpha_frontal)
```



Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ccorr_s_alpha_temporal <- d_ccorr_s_alpha[d_ccorr_s_alpha$ROI == 'temporal',]
d_ccorr_s_alpha_temporal$ROI <- factor(d_ccorr_s_alpha_temporal$ROI)

model_ccorr_s_alpha_temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_alpha_temporal)
summary(model_ccorr_s_alpha_temporal)
```

Subset data to parietal\
model\
summary model\

**parietal**

NO DIFFERENCE

```{r}
d_ccorr_s_alpha_parietal <- d_ccorr_s_alpha[d_ccorr_s_alpha$ROI == 'parietal',]
d_ccorr_s_alpha_parietal$ROI <- factor(d_ccorr_s_alpha_parietal$ROI)

model_ccorr_s_alpha_parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_alpha_parietal)
summary(model_ccorr_s_alpha_parietal)
```

Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ccorr_s_alpha_occipital <- d_ccorr_s_alpha[d_ccorr_s_alpha$ROI == 'occipital',]
d_ccorr_s_alpha_occipital$ROI <- factor(d_ccorr_s_alpha_occipital$ROI)

model_ccorr_s_alpha_occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_alpha_occipital)
summary(model_ccorr_s_alpha_occipital)
```


PLOT CCORR alpha

```{r}
plotIBS <- ggplot(data=d_ccorr_alpha, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('Ccorr alpha')
plotIBS
```

C. beta_\
subset data to ccorr beta_\

```{r}
d_ccorr_beta_ <- d_ccorr[d_ccorr$freq == 'beta_',]
d_ccorr_beta_$freq <- factor(d_ccorr_beta_$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

No DIFFERENCE

```{r}
d_ccorr_beta__frontal <- d_ccorr_beta_[d_ccorr_beta_$ROI == 'frontal',]
d_ccorr_beta__frontal$ROI <- factor(d_ccorr_beta__frontal$ROI)

model_ccorr_beta__frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_beta__frontal)
summary(model_ccorr_beta__frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

DIFFERENCE

```{r}
d_ccorr_beta__temporal <- d_ccorr_beta_[d_ccorr_beta_$ROI == 'temporal',]
d_ccorr_beta__temporal$ROI <- factor(d_ccorr_beta__temporal$ROI)

model_ccorr_beta__temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_beta__temporal)
summary(model_ccorr_beta__temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE

```{r}
d_ccorr_beta__parietal <- d_ccorr_beta_[d_ccorr_beta_$ROI == 'parietal',]
d_ccorr_beta__parietal$ROI <- factor(d_ccorr_beta__parietal$ROI)

model_ccorr_beta__parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_beta__parietal)
summary(model_ccorr_beta__parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

DIFFERENCE

```{r}
d_ccorr_beta__occipital <- d_ccorr_beta_[d_ccorr_beta_$ROI == 'occipital',]
d_ccorr_beta__occipital$ROI <- factor(d_ccorr_beta__occipital$ROI)

model_ccorr_beta__occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ccorr_beta__occipital)
summary(model_ccorr_beta__occipital)
```



subset data to ccorr only sharing

```{r}
d_ccorr_s_beta_ <- d_ccorr_beta_[d_ccorr_beta_$condition == 'ES' | d_ccorr_beta_$condition == 'NS' ,]
d_ccorr_s_beta_$condition <- factor(d_ccorr_s_beta_$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ccorr_s_beta_)){
  if (d_ccorr_s_beta_$condition[irow] == 'ES'){
    d_ccorr_s_beta_$condition_model[irow] <- -.5
  }
  else if (d_ccorr_s_beta_$condition[irow] == 'NS'){
    d_ccorr_s_beta_$condition_model[irow] <- .5
  }
} 


```

Subset data to frontal\
model\
summary model\

**frontal**

DIFFERENCE between orders but not sharing type

```{r}
d_ccorr_s_beta__frontal <- d_ccorr_s_beta_[d_ccorr_s_beta_$ROI == 'frontal',]
d_ccorr_s_beta__frontal$ROI <- factor(d_ccorr_s_beta__frontal$ROI)

model_ccorr_s_beta__frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_beta__frontal)
summary(model_ccorr_s_beta__frontal)
```

Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ccorr_s_beta__temporal <- d_ccorr_s_beta_[d_ccorr_s_beta_$ROI == 'temporal',]
d_ccorr_s_beta__temporal$ROI <- factor(d_ccorr_s_beta__temporal$ROI)

model_ccorr_s_beta__temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_beta__temporal)
summary(model_ccorr_s_beta__temporal)
```

Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE BETWEEN SHARING ORDER BUT NO TYPE OF SHARING. 
Artifact? or something really strange? 
It's between pair comparison, so it simply means that different groups (order of sharing) had different on average IBS, but no differences between types of sharing.

```{r}
d_ccorr_s_beta__parietal <- d_ccorr_s_beta_[d_ccorr_s_beta_$ROI == 'parietal',]
d_ccorr_s_beta__parietal$ROI <- factor(d_ccorr_s_beta__parietal$ROI)

model_ccorr_s_beta__parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_beta__parietal)
summary(model_ccorr_s_beta__parietal)
```

Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ccorr_s_beta__occipital <- d_ccorr_s_beta_[d_ccorr_s_beta_$ROI == 'occipital',]
d_ccorr_s_beta__occipital$ROI <- factor(d_ccorr_s_beta__occipital$ROI)

model_ccorr_s_beta__occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ccorr_s_beta__occipital)
summary(model_ccorr_s_beta__occipital)
```

PLOT CCORR beta_

```{r}
plotIBS <- ggplot(data=d_ccorr_beta_, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('Ccorr beta_')
plotIBS
```


2. ispc.

subset data to ispc.
```{r}
d_ispc. <- d[d$sync == 'ispc.',]
d_ispc.$sync <- factor(d_ispc.$sync)

```

A. theta\
subset data to ispc. theta\

```{r}
d_ispc._theta <- d_ispc.[d_ispc.$freq == 'theta',]
d_ispc._theta$freq <- factor(d_ispc._theta$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

NO DIFFERENCE


```{r}
d_ispc._theta_frontal <- d_ispc._theta[d_ispc._theta$ROI == 'frontal',]
d_ispc._theta_frontal$ROI <- factor(d_ispc._theta_frontal$ROI)

model_ispc._theta_frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._theta_frontal)
summary(model_ispc._theta_frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ispc._theta_temporal <- d_ispc._theta[d_ispc._theta$ROI == 'temporal',]
d_ispc._theta_temporal$ROI <- factor(d_ispc._theta_temporal$ROI)

model_ispc._theta_temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._theta_temporal)
summary(model_ispc._theta_temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

NO DIFFERENCE

```{r}
d_ispc._theta_parietal <- d_ispc._theta[d_ispc._theta$ROI == 'parietal',]
d_ispc._theta_parietal$ROI <- factor(d_ispc._theta_parietal$ROI)

model_ispc._theta_parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._theta_parietal)
summary(model_ispc._theta_parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ispc._theta_occipital <- d_ispc._theta[d_ispc._theta$ROI == 'occipital',]
d_ispc._theta_occipital$ROI <- factor(d_ispc._theta_occipital$ROI)

model_ispc._theta_occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._theta_occipital)
summary(model_ispc._theta_occipital)
```

Sharing comparison

```{r}
d_ispc._s_theta <- d_ispc._theta[d_ispc._theta$condition == 'ES' | d_ispc._theta$condition == 'NS' ,]
d_ispc._s_theta$condition <- factor(d_ispc._s_theta$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ispc._s_theta)){
  if (d_ispc._s_theta$condition[irow] == 'ES'){
    d_ispc._s_theta$condition_model[irow] <- -.5
  }
  else if (d_ispc._s_theta$condition[irow] == 'NS'){
    d_ispc._s_theta$condition_model[irow] <- .5
  }
} 


```

Subset data to frontal\
model\
summary model\

**frontal**

NO DIFFERENCE

```{r}
d_ispc._s_theta_frontal <- d_ispc._s_theta[d_ispc._s_theta$ROI == 'frontal',]
d_ispc._s_theta_frontal$ROI <- factor(d_ispc._s_theta_frontal$ROI)

model_ispc._s_theta_frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_theta_frontal)
summary(model_ispc._s_theta_frontal)
```

Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ispc._s_theta_temporal <- d_ispc._s_theta[d_ispc._s_theta$ROI == 'temporal',]
d_ispc._s_theta_temporal$ROI <- factor(d_ispc._s_theta_temporal$ROI)

model_ispc._s_theta_temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_theta_temporal)
summary(model_ispc._s_theta_temporal)
```

Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE

```{r}
d_ispc._s_theta_parietal <- d_ispc._s_theta[d_ispc._s_theta$ROI == 'parietal',]
d_ispc._s_theta_parietal$ROI <- factor(d_ispc._s_theta_parietal$ROI)

model_ispc._s_theta_parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_theta_parietal)
summary(model_ispc._s_theta_parietal)
```

Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ispc._s_theta_occipital <- d_ispc._s_theta[d_ispc._s_theta$ROI == 'occipital',]
d_ispc._s_theta_occipital$ROI <- factor(d_ispc._s_theta_occipital$ROI)

model_ispc._s_theta_occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_theta_occipital)
summary(model_ispc._s_theta_occipital)
```




PLOT ispc. THETA

```{r}
plotIBS <- ggplot(data=d_ispc._theta, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('ispc. theta')
plotIBS
```

B. alpha\
subset data to ispc. alpha\

```{r}
d_ispc._alpha <- d_ispc.[d_ispc.$freq == 'alpha',]
d_ispc._alpha$freq <- factor(d_ispc._alpha$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

DIFFERENCE!

```{r}
d_ispc._alpha_frontal <- d_ispc._alpha[d_ispc._alpha$ROI == 'frontal',]
d_ispc._alpha_frontal$ROI <- factor(d_ispc._alpha_frontal$ROI)

model_ispc._alpha_frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._alpha_frontal)
summary(model_ispc._alpha_frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

DIFFERENCE

```{r}
d_ispc._alpha_temporal <- d_ispc._alpha[d_ispc._alpha$ROI == 'temporal',]
d_ispc._alpha_temporal$ROI <- factor(d_ispc._alpha_temporal$ROI)

model_ispc._alpha_temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._alpha_temporal)
summary(model_ispc._alpha_temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE!

```{r}
d_ispc._alpha_parietal <- d_ispc._alpha[d_ispc._alpha$ROI == 'parietal',]
d_ispc._alpha_parietal$ROI <- factor(d_ispc._alpha_parietal$ROI)

model_ispc._alpha_parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._alpha_parietal)
summary(model_ispc._alpha_parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

DIFFERENCE!

```{r}
d_ispc._alpha_occipital <- d_ispc._alpha[d_ispc._alpha$ROI == 'occipital',]
d_ispc._alpha_occipital$ROI <- factor(d_ispc._alpha_occipital$ROI)

model_ispc._alpha_occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._alpha_occipital)
summary(model_ispc._alpha_occipital)
```


We follow up with differences between sharing
subset data to ispc. only sharing

```{r}
d_ispc._s_alpha <- d_ispc._alpha[d_ispc._alpha$condition == 'ES' | d_ispc._alpha$condition == 'NS' ,]
d_ispc._s_alpha$condition <- factor(d_ispc._s_alpha$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ispc._s_alpha)){
  if (d_ispc._s_alpha$condition[irow] == 'ES'){
    d_ispc._s_alpha$condition_model[irow] <- -.5
  }
  else if (d_ispc._s_alpha$condition[irow] == 'NS'){
    d_ispc._s_alpha$condition_model[irow] <- .5
  }
} 


```

Subset data to frontal\
model\
summary model\

**frontal**

NO DIFFERENCE

```{r}
d_ispc._s_alpha_frontal <- d_ispc._s_alpha[d_ispc._s_alpha$ROI == 'frontal',]
d_ispc._s_alpha_frontal$ROI <- factor(d_ispc._s_alpha_frontal$ROI)

model_ispc._s_alpha_frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_alpha_frontal)
summary(model_ispc._s_alpha_frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ispc._s_alpha_temporal <- d_ispc._s_alpha[d_ispc._s_alpha$ROI == 'temporal',]
d_ispc._s_alpha_temporal$ROI <- factor(d_ispc._s_alpha_temporal$ROI)

model_ispc._s_alpha_temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_alpha_temporal)
summary(model_ispc._s_alpha_temporal)
```


Subset data to parietal\
model\
summary model\

**parietal**

NO DIFFERENCE

```{r}
d_ispc._s_alpha_parietal <- d_ispc._s_alpha[d_ispc._s_alpha$ROI == 'parietal',]
d_ispc._s_alpha_parietal$ROI <- factor(d_ispc._s_alpha_parietal$ROI)

model_ispc._s_alpha_parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_alpha_parietal)
summary(model_ispc._s_alpha_parietal)
```

Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ispc._s_alpha_occipital <- d_ispc._s_alpha[d_ispc._s_alpha$ROI == 'occipital',]
d_ispc._s_alpha_occipital$ROI <- factor(d_ispc._s_alpha_occipital$ROI)

model_ispc._s_alpha_occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_alpha_occipital)
summary(model_ispc._s_alpha_occipital)
```


PLOT ispc. alpha

```{r}
plotIBS <- ggplot(data=d_ispc._alpha, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('ispc. alpha')
plotIBS
```

C. beta_\
subset data to ispc. beta_\

```{r}
d_ispc._beta_ <- d_ispc.[d_ispc.$freq == 'beta_',]
d_ispc._beta_$freq <- factor(d_ispc._beta_$freq)
```

Subset data to frontal\
model\
summary model\

**FRONTAL**\

DIFFERENCE

```{r}
d_ispc._beta__frontal <- d_ispc._beta_[d_ispc._beta_$ROI == 'frontal',]
d_ispc._beta__frontal$ROI <- factor(d_ispc._beta__frontal$ROI)

model_ispc._beta__frontal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._beta__frontal)
summary(model_ispc._beta__frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

DIFFERENCE

```{r}
d_ispc._beta__temporal <- d_ispc._beta_[d_ispc._beta_$ROI == 'temporal',]
d_ispc._beta__temporal$ROI <- factor(d_ispc._beta__temporal$ROI)

model_ispc._beta__temporal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._beta__temporal)
summary(model_ispc._beta__temporal)
```
Subset data to parietal\
model\
summary model\

**parietal**

DIFFERENCE

```{r}
d_ispc._beta__parietal <- d_ispc._beta_[d_ispc._beta_$ROI == 'parietal',]
d_ispc._beta__parietal$ROI <- factor(d_ispc._beta__parietal$ROI)

model_ispc._beta__parietal <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._beta__parietal)
summary(model_ispc._beta__parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

DIFFERENCE

```{r}
d_ispc._beta__occipital <- d_ispc._beta_[d_ispc._beta_$ROI == 'occipital',]
d_ispc._beta__occipital$ROI <- factor(d_ispc._beta__occipital$ROI)

model_ispc._beta__occipital <- lmer(IBS ~  Sharing  + (1|pair), data=d_ispc._beta__occipital)
summary(model_ispc._beta__occipital)
```

We follow up with differences between sharing conditions and their order only for parietal

subset data to ispc. only sharing

```{r}
d_ispc._s_beta_ <- d_ispc._beta_[d_ispc._beta_$condition == 'ES' | d_ispc._beta_$condition == 'NS' ,]
d_ispc._s_beta_$condition <- factor(d_ispc._s_beta_$condition)

# e -.5
# n  .5

for (irow in 1:nrow(d_ispc._s_beta_)){
  if (d_ispc._s_beta_$condition[irow] == 'ES'){
    d_ispc._s_beta_$condition_model[irow] <- -.5
  }
  else if (d_ispc._s_beta_$condition[irow] == 'NS'){
    d_ispc._s_beta_$condition_model[irow] <- .5
  }
} 


```

Subset data to frontal\
model\
summary model\

**frontal**

NO DIFFERENCE

```{r}
d_ispc._s_beta__frontal <- d_ispc._s_beta_[d_ispc._s_beta_$ROI == 'frontal',]
d_ispc._s_beta__frontal$ROI <- factor(d_ispc._s_beta__frontal$ROI)

model_ispc._s_beta__frontal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_beta__frontal)
summary(model_ispc._s_beta__frontal)
```
Subset data to temporal\
model\
summary model\

**temporal**

NO DIFFERENCE

```{r}
d_ispc._s_beta__temporal <- d_ispc._s_beta_[d_ispc._s_beta_$ROI == 'temporal',]
d_ispc._s_beta__temporal$ROI <- factor(d_ispc._s_beta__temporal$ROI)

model_ispc._s_beta__temporal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_beta__temporal)
summary(model_ispc._s_beta__temporal)
```


Subset data to parietal\
model\
summary model\

**parietal**

NO DIFFERENCE

```{r}
d_ispc._s_beta__parietal <- d_ispc._s_beta_[d_ispc._s_beta_$ROI == 'parietal',]
d_ispc._s_beta__parietal$ROI <- factor(d_ispc._s_beta__parietal$ROI)

model_ispc._s_beta__parietal <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_beta__parietal)
summary(model_ispc._s_beta__parietal)
```
Subset data to occipital\
model\
summary model\

**occipital**

NO DIFFERENCE

```{r}
d_ispc._s_beta__occipital <- d_ispc._s_beta_[d_ispc._s_beta_$ROI == 'occipital',]
d_ispc._s_beta__occipital$ROI <- factor(d_ispc._s_beta__occipital$ROI)

model_ispc._s_beta__occipital <- lmer(IBS ~  condition_model*SharingOrder  + (1|pair), data=d_ispc._s_beta__occipital)
summary(model_ispc._s_beta__occipital)
```

PLOT ispc. beta_

```{r}
plotIBS <- ggplot(data=d_ispc._beta_, aes(x=condition, y=IBS, fill=condition))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(FirstSharing~ROI)+
  theme_bw()+
  ggtitle('ispc. beta_')
plotIBS
```

ADDITIONAL PLOTS

CCORR

Here I would like to point (visually) that differences (statistical) between resting state 1 (baseline) are not in our favor. Only in Theta (frontal, temporal) IBS is higher in Sharing conditions than Baseline. 
In alpha (all ROIs) and beta (temporal, parietal, occipital) IBS is higher in baseline. 

```{r}
d_ccorr <- d[d$sync == 'ccorr',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```

ISPC

Parietal difference in alpha and beta is also stronger for baseline than sharing conditions


```{r}
d_ccorr <- d[d$sync == 'ispc.',]


plotIBS <- ggplot(data=d_ccorr, aes(x=SharingPLOT, y=IBS, fill=SharingPLOT))+
  geom_violin()+
  geom_tufteboxplot()+
  facet_grid(freq~ROI)+
  theme_bw()
plotIBS
```


